Consistent Polyhedral Surrogates via Embedding

### 2019-07-29 notes/top-k.tex
Fixed typo and added detail on Bayes Risk

We can now write the expected loss as follows:
\begin{align*}
\inprod{p}{L^{top-k}(u)} &= \sum_{y=1}^n p_y L^{top-k}(u)_y \\
&= \sum_{y=1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
&= \sum_{y=1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1-u_y + \ubar)\\
&= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac u k}\\
&= 1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)}
\end{align*}
When considering the Bayes Risk, we use this final form of the expected loss.

\subsection{Bayes Risk}
First, consider the case where $u_y = 0$ and $u'_y = 1$, with $u_j = u'_j \;\forall i \neq j$.
As the expected loss is linear on $u_y$, and these are the boundary cases, we know that $u$ is optimal on one of these two reports in this case.

So we ask when is $\inprod{p}{L^{top-k}(u)} \leq \inprod{p}{L^{top-k}(u')}$?
\begin{align*}
1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
- \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq \frac {1}{k} - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
0 &\leq \frac{1}{k} - p_y(\frac{k+1}{k})\\
p_y &\leq \frac{1}{k+1}
\end{align*}

Conversely, if $p_y > \frac{1}{k+1}$, it is to better to report $u_y = 1$ than $u_y = 0$.
However, since we are not restricted to the unit hypercube, we might ask when it is optimal to bring $u_y = 1$ up to $u'_y = 1 + \epsilon$ given $\epsilon > 0$.
Here, we consider when $\inprod{p}{L^{top-k}(u)} \leq \inprod{p}{L^{top-k}(u')}$.
\begin{align*}
1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
\frac{1}{k} - p_y (\frac{k+1}{k}) &\leq \frac{1+\epsilon}{k} - p_y (\frac{k+1}{k}(1 + \epsilon))\\
p_y &\leq \frac{1}{k}
\end{align*}
In this case, $u_y=1$ is preferable to $u+y >1$.
If $p_y > \frac 1 k$, then we want to push $u_y$ as high as we can, but recall that we restrict to $u_y \leq \ubar_{-y} + 1$.
Because the upper bound on $u_y$ depends on $\ubar$, we can't determine $u$ iteratively.
However, we can construct $u$ as given below.
\begin{conjecture}
	Fix $p \in \simplex$.
	Let $g_t = |\{p_i : p_i \geq \frac 1 k\}|$ and $g_b = | \{p_i \in (\frac{1}{k+1}, \frac{1}{k})\}|$.
	The property \[\gamma(p) = 
	\left[
	\begin{cases}
	0 & p_i \leq \frac {1}{k+1}\\
	1 & p_i \in (\frac{1}{k+1}, \frac{1}{k})\\
	\frac{g_b + k-1}{k-g_t} & o/w
	\end{cases}
	\right]_{i=1}^n
	\] refines the property $\prop{L^{top-k}}$.
\end{conjecture}
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

We can now write the expected loss as follows:
\begin{align*}
\inprod{p}{L^{top-k}(u)} &= \sum_{y=1}^n p_y L^{top-k}(u)_y \\
&= \sum_{y=1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
&= \sum_{y=1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1 + \ubar)\\
&= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq b}}{\frac 1 k \ones} - \inprod{p \odot \Ind{b+1 \leq y \leq k}}{ \frac u k}\\
&= 1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)}
\end{align*}
When considering the Bayes Risk, we use this final form of the expected loss.

\subsection{Bayes Risk}
Now we consider minimizing the expected loss given above.
Since the expected loss is linear, we can look at each outcome $y$ and when the coefficient of $u_y$ is positive and negative.
In essence, this is the subgradient in the $u_y$ direction, and so we can see when $L^{top-k}$ is increasing as a function if $u_y$ by evaluating when the sign of $u_y$'s coefficient.

Given our final form of $L^{top-k}$, the coefficient of $u_y$ is $\frac 1 k - p_y(\frac {k+1}{k})$ if $u_y \in [0,1]$, and $\frac 1 k - p_y$ if $u_y > 1$.

If $p_y \leq \frac 1 {k+1}$, this coefficient is nonnegative in both cases, so we want to set $u_y = 0$.
If $p_y \in [\frac 1 {k+1}, \frac 1 k]$, the coefficient is nonpositive in the first case, and nonnegative in the second, so we want to set $u_y = 1$.
If $p_y \geq \frac 1 k$, then the coefficient is nonpositive in both cases, so we want to set $u$ as high as permitted.
%First, consider the case where $u_y = 0$ and $u'_y = 1$, with $u_j = u'_j \;\forall i \neq j$.
%As the expected loss is linear on $u_y$, and these are the boundary cases, we know that $u$ is optimal on one of these two reports in this case.
%
%So we ask when is $\inprod{p}{L^{top-k}(u)} \leq \inprod{p}{L^{top-k}(u')}$?
%\begin{align*}
%1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
%- \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq \frac {1}{k} - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
%0 &\leq \frac{1}{k} - p_y(\frac{k+1}{k})\\
%p_y &\leq \frac{1}{k+1}
%\end{align*}
%
%Conversely, if $p_y > \frac{1}{k+1}$, it is to better to report $u_y = 1$ than $u_y = 0$.
%However, since we are not restricted to the unit hypercube, we might ask when it is optimal to bring $u_y = 1$ up to $u'_y = 1 + \epsilon$ given $\epsilon > 0$.
%Here, we consider when $\inprod{p}{L^{top-k}(u)} \leq \inprod{p}{L^{top-k}(u')}$.
%\begin{align*}
%1 + \ubar - \inprod{p}{u + \frac 1 k \min(u, \ones)} &\leq 1 + \ubar' - \inprod{p}{u' + \frac 1 k \min(u', \ones)}\\
%\frac{1}{k} - p_y (\frac{k+1}{k}) &\leq \frac{1+\epsilon}{k} - p_y (\frac{k+1}{k}(1 + \epsilon))\\
%p_y &\leq \frac{1}{k}
%\end{align*}
%In this case, $u_y=1$ is preferable to $u+y >1$.
%If $p_y > \frac 1 k$, then we want to push $u_y$ as high as we can, but recall that we restrict to $u_y \leq \ubar_{-y} + 1$.
%Because the upper bound on $u_y$ depends on $\ubar$, we can't determine $u$ iteratively.

However, we can construct $u$ as given below.
\begin{conjecture}
	Fix $p \in \simplex$.
	Let $g_t = |\{p_i : p_i \geq \frac 1 k\}|$ and $g_s = | \{p_i \in (\frac{1}{k+1}, \frac{1}{k})\}|$.
	The property \[\gamma(p) = 
	\left[
	\begin{cases}
	0 & p_i \leq \frac {1}{k+1}\\
	1 & p_i \in (\frac{1}{k+1}, \frac{1}{k})\\
	\frac{g_s + k-1}{k-g_t} & o/w
	\end{cases}
	\right]_{i=1}^n
	\] refines the property $\prop{L^{top-k}}$.
\end{conjecture}
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
